\phantomsection
\addcontentsline{toc}{section}{References}

\begin{thebibliography}{30}

    \bibitem{1api}
    Abid, E. B. (2022). \emph{What Is An API In Image Processing?}. APILayer Blog.
    \href{https://blog.apilayer.com/what-is-an-api-in-image-processing/}{https://blog.apilayer.com/what-is-an-api-in-image-processing/}

    \bibitem{adand}
    Adyanthaya, S. K. (2020). \emph{Text Recognition from Images: A Study. International Journal of 
    Engineering Research \& Technology, 8(13)}.
    \href{https://www.ijert.org/text-recognition-from-images-a-study}{https://www.ijert.org/text-recognition-from-images-a-study}

    \bibitem{2imgprocess}
    Anbarjafari, G. (2014). \emph{Digital Image Processing}. University of Tartu.
    \href{https://sisu.ut.ee/imageprocessing/book/1}{https://sisu.ut.ee/imageprocessing/book/1}

    \bibitem{3patreg}
    Ansari. (2023). \emph{Pattern Recognition \textbar{} Introduction}. GeeksforGeeks.
    \href{https://www.geeksforgeeks.org/pattern-recognition-introduction/}{https://www.\\geeksforgeeks.org/pattern-recognition-introduction/}

    \bibitem{4textsearch}
    \emph{Apps with “Full-Text Search” feature}. (2023). AlternativeTo.
    \href{https://alternativeto.net/feature/full-text-search/}{https://alternativeto\\.net/feature/full-text-search/}

    \bibitem{5bmrsgate}
    Borah, P. P., Talukdar, G., \& Jayanta, Y. (2013). \emph{A comparison of String matching
    algorithms-Boyer-Moore algorithm and Brute-Force algorithm}. ResearchGate.
    \href{https://www.researchgate.net/publication/265251889_A_comparison_of_String_matching_algorithms-Boyer-Moore_algorithm_and_Brute-Force_algorithm}{https://www.researchgate.net/publication/265251889\_A\_comparison\_\\of\_String\_matching\_algorithms-Boyer-Moore\_algorithm\_and\_Brute-Force\_algorithm}

    \bibitem{6appbm}
    Buslim, N., Faradita, D. T., Anif, S., \& Masruroh, S. U. (2020). \emph{Mobile Based Application
    “Hadith for Women” Using Algorithm Boyer Moore}.
    \href{https://doi.org/10.4108/eai.7-11-2019.2294564}{https://doi.org/10.4108/eai.7-11-2019.2294564}

    \bibitem{7ebooks}
    Cordón-García, J., Alonso-Arévalo, J., Gómez-Díaz, R., \& Linder, D. F. (2013). \emph{Open access
    eBooks}. In Elsevier eBooks (pp. 121–141).
    \href{https://doi.org/10.1016/b978-1-84334-726-2.50004-5}{https://doi.org/10.1016/b978-1-84334-726-2.50004-5}

    \bibitem{8kmpbm}
    Dawood, S. S., \& Barakat, S. A. (2020, May 19). \emph{Empirical Performance Evaluation Of Knuth
    Morris Pratt And Boyer Moore String Matching Algorithms}.
    \href{https://journal.uod.ac/index.php/uodjournal/article/view/732/560}{https://journal.uod.ac/index.php/uodjournal/article/view/732/560}

    \bibitem{9fts}
    \emph{Full Text Search \textbar{} FileCenter DMS}. (2023). Filecenter. 
    \href{https://www.filecenter.com/info-text-search.html#:~:text=In\%20a\%20nutshell\%2C\%20full\%20text,merely\%20searching\%20the\%20file\%20nameS}{https://www.filecenter.com\\/info-text-search}

    \bibitem{10howitworksfts}
    Stasilovich, S. (2018) Issart.com.
    \href{https://blog.issart.com/full-text-search-how-it-works/}{https://blog.issart.com\\/full-text-search-how-it-works/}

    \bibitem{11mongodbfts}
    \emph{Full-Text Search: What Is It And How It Works \textbar{} MongoDB}. (2023). MongoDB.
    \href{https://www.mongodb.com/basics/full-text-search}{https://www.mongodb.com/basics/full-text-search}

    \bibitem{12gfgsma}
    GeeksforGeeks. (2022). \emph{Applications of String Matching Algorithms}. GeeksforGeeks.
    \href{https://www.geeksforgeeks.org/applications-of-string-matching-algorithms/}{https://www.geeksforgeeks.org/applications-of-string-matching-algorithms/}

    \bibitem{trvw}
    How does text recognition work. (n.d.). \emph{How Does Text Recognition Work}.
    \href{https://toloka.ai/blog/how-does-text-recognition-work/}{https://toloka.ai/blog/how-does-text-recognition-work/}

    \bibitem{13kmpbmcomp}
    Khumaidi, A., Ronisah, Y. A., \& Putro, H. P. (2020). \emph{Comparison of Knuth Morris Pratt and
    Boyer Moore algorithms for a web-based dictionary of computer terms}. Jurnal Informatika, 14(1), 7. 
    \href{https://doi.org/10.26555/jifo.v14i1.a17038}{https://doi.org/10.26555/jifo.v14i1.a17038}

    \bibitem{14comparativeanal}
    Layustira, V. A., \& Istiono, W. (2021). \emph{Comparative Analysis of Brute Force and Boyer
    Moore Algorithms in Word Suggestion Search}. International Journal of Emerging Trends in
    Engineering Research, 9(8), 1064–1068. 
    \href{https://doi.org/10.30534/ijeter/2021/05982021}{https://doi.org/10.30534/ijeter/2021/05982021}

    \bibitem{15studybm}
    Lin, L. L., \& Soe, M. T. (2020). \emph{A Comparative Study on Brute-Force String Matching and
    Boyer- Moore String Matching}. Journal of Science and Technology for Sustainable Development, 1.
    \href{https://www.uit.edu.mm/storage/2021/01/1-LLL.pdf}{https://www.uit.edu.mm/storage/2021/01/1-LLL.pdf}

    \bibitem{16comp2}
    Rasool, A., Tiwari, A., Singla, G., \& Khare, N. (2012). \emph{String Matching Methodologies: A
    Comparative Analysis}. International Journal of Computer Science and Information Technologies, 3. 
    \href{https://www.researchgate.net/publication/268273984_String_Matching_MethodologiesA_Comparative_Analysis}{https://www.researchgate.net/publication/268273984\_String\_Matching\_\\MethodologiesA\_Comparative\_Analysis}

    \bibitem{17intro}
    Sam, S. (2019). \emph{Introduction to Pattern Searching Algorithms}. Tutorials Point.
    \href{https://www.tutorialspoint.com/introduction-to-pattern-searching-algorithms#:~:text=Pattern\%20Searching\%20algorithms\%20are\%20used,task\%20for\%20a\%20longer\%20text}{https://www.tutorialspoint.com/introduction-to-pattern-searching-algorithms}

    \bibitem{18finger}
    Supatmi, S., \& Sumitra, I. D. (2019). \emph{Fingerprint Identification using Bozorth and
    Boyer-Moore Algorithm}. IOP Conference Series.
    \href{https://doi.org/10.1088/1757-899x/662/2/022040}{https://doi.org/10.1088/1757-899x/662/2/022040}

    \bibitem{19bmappli}
    Waruwu, F. T. (2017). \emph{Application Of Boyer Moore Algorithm for Text Searching}.
    International Journal of Informatics and Computer Science, 1(1).
    \href{https://www.semanticscholar.org/paper/Application-Of-Boyer-Moore-Algorithm-for-Text-Waruwu/423dcabcd3c5a5e5187f33726114d98e51c14a5c}{https://www.semanticscholar.org/paper/Application-Of-Boyer-Moore-Algorithm-for-Text-Waruwu/}

    \bibitem{20patrego}
    Wigmore, I. (2018). \emph{pattern recognition}. WhatIs.com.
    \href{https://www.techtarget.com/whatis/definition/pattern-recognition}{https://www.techtarget.com\\/whatis/definition/pattern-recognition}

    \bibitem{arini}
    Arini, A., \& Suseno, H. B. (2019). \emph{Application of the boyer moore method in the
        application dictionary of web-based information technology terms (case study: pt. erefka
    tiga pilar utama)}. INTEGRATED (Journal of Information Technology and Vocational Education),
    1(2), 29–36. \href{https://ejournal.upi.edu/index.php/integrated/article/view/21995}{https://ejournal.upi.edu/index.php/integrated/article/view/21995}

    \bibitem{fitriyah}
    Fitriyah, F., Gayo, W. R. P., Handayani, A. N., Wibawa, A. P., \& Kurniawan, F. (2020).
    \emph{The Implementation of Boyer-Moore Algorithm in WEB Based Computer and Informatic Terms
    Dictionary}. \href{https://doi.org/10.1109/icovet50258.2020.9230344}{https://doi.org/10.1109/icovet50258.2020.9230344}

    \bibitem{satpuri}
    Saputri, W. S., Dhenabayu, R., \& Febrinita, F. (2018). \emph{APPLICATION OF STRING MATCHING
    USING BOYER MOORE ALGORITHM IN THE APPLICATION OF DICTIONARY LIVESTOCK TERMS}.
    \href{https://doi.org/10.35457/josar.v1i01.614}{https://doi.org/10.35457/josar.v1i01.614}

    \bibitem{boyermooregfg}
    GeeksforGeeks. (2022). \emph{Boyer Moore Algorithm for Pattern Searching}. GeeksforGeeks.
    \href{https://www.geeksforgeeks.org/boyer-moore-algorithm-for-pattern-searching/?ref=lbp}{https://www.geeksforgeeks.org/boyer-moore-algorithm-for-pattern-searching/?ref=lbp}

\end{thebibliography}
